Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-09-22 writeup/RochatEtal_ResponseToReviewers.tex

\item {\it (Section 4) I find “jPDF” odd. Try “joint-PDF” or “PDF” in general.}\\

We changed jPDF with joint-PDF; it does look much better.

\item {\it (Section 4, last paragraph) ``...whereas divergence is moderately, negatively skewed as
        predicted by ...'' Specifically mention convergence/downwelling.}

        \bdp
            We added ``convergence/downwelling'' to the text (line xx).
        \edp

@@

\item {\it (Figure 2) Is the mean of the strain rate zero? Is the mean of the divergence zero? The
        variance should be used rather than the root-mean-squared (RMS).}

        \bdp
            At every snapshot, the horizontally-averaged divergence is nearly zero;
            the strain rate horizontal average is not zero, because by definition
            $\alpha \ge 0$. The (normalized) RMS better characterizes the the bulk
            gradient Rossby number of the flow.
        \edp

\item {\it (Figure 2) What is the sensitivity of the estimates to the stencil type? See Arbic et al.
        paper describing this sensitivity for satellite altimetry.}

        \bdp
            To asses the error of centered second-order scheme we periodized
            our domain with reflections. Statistics of lateral velocity gradients
            obtained via spectral differentiation are 10-15$\%$ larger than the ones
            obtained using second-order finite differences. But there are no qualitative
            changes to Figure 2 and no changes in our conclusions. For simplicity, we
            opt to use finite differences. We now report this estimate of accuracy of
            our finite difference scheme (lines xx-xx).
        \edp

### 2016-09-22 writeup/rocha_etal.tex
Significant changes to the abstract

\begin{abstract}
    We provide evidence  of
    vigorous modulation of near-surface dynamics at submesoscales
    (10-100 km) in the Kuroshio Extension. The analysis uses outputs of general
    circulation models spun-up from a state estimate and forced by high-frequency
    winds, surface fluxes, and tides.
    Consistent with recent studies, deep late-winter mixed layers
    are prone to shallow baroclinic instabilities and submesoscale turbulence
    prevails in late winter/early spring. Summertime
    re-stratification, however, weakens submesoscale turbulence and enhances submesoscale inertia-gravity
     waves near the surface. In the Kuroshio Extension,
    inertia-gravity waves dominate the submesoscale surface kinetic energy and
    sea-surface height (SSH) variance in late summer/early fall, with implications for
    the accuracy of surface geostrophic currents diagnosed from SSH measured by
    high-resolution satellite altimeters.
\end{abstract}

@@

 Time series of PDFs of vorticity and divergence (supporting information) show
 a strong oscillation between these two regimes. In late winter/early spring
 the vorticity is strongly positively skewed, whereas the divergence is moderately
 negatively skewed (convergence/downwelling) as predicted by frontogenesis \citep[e.g., ][]{mcwilliams2016}.
 In late summer/early fall, the divergence is stronger, but PDFs are much less skewed,
consistent with linear IGWs.

>>>>

\begin{abstract}
    Submesoscale turbulence, fueled by ample potential
    energy stored in wintertime deep mixed layers, undergoes vigorous seasonality.
    Here we provide model evidence that the seasonally-changing upper-ocean
    stratification also modulates submesoscale --- here 10-100 km ---
    inertia-gravity waves. Summertime re-stratification weakens submesoscale
    turbulence but enhances inertia-gravity waves near the surface. Thus,
    submesoscale turbulence and inertia-gravity waves undergo vigorous out-of-phase
    seasonal cycles. The present results imply a strong seasonal modulation of
    the skill and accuracy of geostrophic velocity diagnostics from submesoscale
    sea-surface height delivered by the Surface and Water Ocean Topography (SWOT)
    satellite mission
\end{abstract}

@@

 Time series of PDFs of vorticity and divergence (supporting information) show
 a strong oscillation between these two regimes. In late winter/early spring
 the vorticity is strongly positively skewed, whereas the divergence is moderately
 negatively skewed (convergence/downwelling) as predicted by frontogenesis \citep[e.g., ][]{mcwilliams2016}.
 In late summer/early fall, the divergence is stronger, but PDFs are much less skewed,
consistent with a superposition of random linear IGWs \citep[e.g.,][]{garrett_munk1972}.
